DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-09-07 manuscript/manuscript.Rmd
add footnote for deeptriangle name

In developing our framework, which we call DeepTriangle, we also draw inspiration from the existing stochastic reserving literature. Works that propose utilizing data in addition to paid losses include @quarg2004munich, which uses incurred losses, and @miranda2012double, which incorporates claim count information. Moving beyond a single homogeneous portfolio, @avanzi2016stochastic considers the dependencies among lines of business within an insurer's portfolio, and @peremans2018robust proposes a robust general multivariate chain ladder approach to accommodate outliers. There is also a category of models, referred to as state space or adaptive models, that allow parameters to evolve recursively in time as more data is observed [@chukhrova2017state]. This iterative updating mechanism is analogous to the recurrent neural network architecture presented in this paper.

>>>>

In developing our framework, which we call DeepTriangle[^2], we also draw inspiration from the existing stochastic reserving literature. Works that propose utilizing data in addition to paid losses include @quarg2004munich, which uses incurred losses, and @miranda2012double, which incorporates claim count information. Moving beyond a single homogeneous portfolio, @avanzi2016stochastic considers the dependencies among lines of business within an insurer's portfolio, while @peremans2018robust proposes a robust general multivariate chain ladder approach to accommodate outliers. There is also a category of models, referred to as state space or adaptive models, that allow parameters to evolve recursively in time as more data is observed [@chukhrova2017state]. This iterative updating mechanism is similar in spirit to the continuous updating of neural network weights during model deployment.

[^2]: A portmanteau of *deep learning* and *loss development triangle*
